Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-14 icse/paper.tex
Extract method

\subsubsection{Contents}
% The rationale for our categories regarding clone contents.
The contents of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the contents of clones:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

\subsection{Refactoring}
CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section...

\subsubsection{Extract Method}
Show my categories to show what clones can be dealt with by method extraction.

>>>>

\subsubsection{Contents}\label{sec:contents}
% The rationale for our categories regarding clone contents.
The contents of a clone instance determine what refactoring techniques can be applied to refactor such clones. We define the following categories by which we analyze the contents of clones:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

\subsection{Refactoring}
CloneRefactor can refactor clones using the ``Extract Method'' refactoring technique. In this section we show which clones we refactor and how we apply these transformations.

\subsubsection{Extract Method}
There are several influencing factors that may obstruct the possibility to extract code to a new method:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a block statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of Sec.~\ref{sec:contents}, the ``Extract Method'' refactoring technique cannot be applied.
    \item \textbf{Returns multiple values}: If a clone modifies or declares multiple pieces of data that it should return.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}
Clones that do not fall in the \textit{Can Be Extracted} category may require additional transformations or other techniques to refactor. CloneRefactor only refactors the clones that \textit{Can Be Extracted}.
